---
title: "Class 10"
author: "Andrew Rauscher"
date: "2026-09-28"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
    code_folding: show
    code_download: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Robotstxt

The code chunk below will show the output from the [robotstxt package] () for the ISA course bulletin  available at: 
<https://bulletin.miamioh.edu/courses-instruction/isa/index.html>

```{r}
robotstxt::paths_allowed(paths = "/courses-instruction/isa/", domain = "bulletin.miamioh.edu", bot = "*")
```
# Practice

From the chuck below, we are allowed to scrape the [MU Football wiki page] (<https://en.wikipedia.org/wiki/Miami_RedHawks_football>)
```{r}
robotstxt::paths_allowed(paths = "wiki/", domain = "https://en.wikipedia.org/wiki/Miami_RedHawks_football", bot = "*")
```

## 'robotstxt' demo:linkedin

```{r linkedin}
robotstxt::paths_allowed(paths = "jobs/", domain = "https://www.linkedin.com/", bot = "*")
```

If you removed the slash after the '.com', the warning disappeared and we got a consistent result with the linkedin page.

## 'rvest' demo: ISA course bulletin

```{r rvest_demo}
isa_page_in_r = rvest::read_html("https://bulletin.miamioh.edu/courses-instruction/isa/")

# Extract the titles
# If all titles look the same on the page, it means that they have the same tag/class, which would allow you to extract them in one step
# We got the selector below by:
## [a] highlighted the course
## [b] right clicked and selected inspect
## [c] found the part that was flushed containing the title
## [d] right clicked and copied the selector
## [e] I saw that the output from the code below just got me the 24th course so I dropped the ':nth-child(24)
isa_page_in_r |> 
  rvest::html_elements(
  "#sc_sccoursedescs > div > p.courseblocktitle > strong"
) |>
  rvest::html_text2() -> isa_titles

#Course descriptions
# Css selector obtained using the selector gadget
isa_page_in_r |>
  rvest::html_elements(".courseblockdesc") |>
  rvest::html_text2() -> isa_descs

isa_df = data.frame(
  title = isa_titles, description = isa_descs
)
```

















