---
title: "Class 11"
author: "Andrew Rauscher"
date: "2026-09-30"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
    code_folding: show
    code_download: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Learning Objectives for Today

- Scrape multiple webpages using 'for' loops;

- Scrape ,multiple webpages using the 'purrr::map()' type functions, which would also make you write your own custom functions in R.

## Extending the Course Bulletin Scrape for multiple departments

For the sake of this example, let us scrape the following pages:
[ISA](https://bulletin.miamioh.edu/courses-instruction/isa/) and
[MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/)


From the logic shown in class, you can essentially do that for all FDB departments


Note that if you are doing it for just a few departments, you can just repeat your code a few times; howwever, this is bad practice so we will not do this in class. Software engineers tend to refer to this as: **DRY** (dont repeat yourself).

```{r bulletin}
dept_abbr = c('acc', 'bus', 'isa', 'mkt') # Extending the example to 4 depts
# Line below illustrates how the url can be constructed by pasting0 (i.e, no space) the base_url, dept_abbreviation and the forward slash

courses_df = data.frame() # Initialize the container
for (dept_name in dept_abbr) {
  cat(rep("-",25))
  print(dept_name)
  dept_url = paste0(
    "https://bulletin.miamioh.edu/courses-instruction/", dept_name, "/")
  
  # For the titles, I will use the selector gadget and for the desc, I will use the inspector (to show you alternative CSS selectors for what we did on Mon)
  webpage = rvest::read_html(dept_url)
  
  webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
  webpage |> 
    rvest::html_elements("#sc_sccoursedescs > div > p.courseblockdesc") |>
  rvest::html_text2() -> descs
  
  df = data.frame(title = titles, desc = descs)
  df$title[1] |> print() # Showing only the first course title
  
  courses_df = rbind(courses_df, df)
  cat(rep("-", 25))
}
```


## Re-Examining the Prior Example with the 'purrr' package

My preferred approach with the purrr functions is to first createe my own function and then use it within the package

```{r}
scrape_mu_bulletin = function(dept_url){

  webpage = rvest::read_html(dept_url)
  
  webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
  webpage |> 
    rvest::html_elements("#sc_sccoursedescs > div > p.courseblockdesc") |>
    rvest::html_text2() -> descs
  
  df = data.frame(title = titles, desc = descs)
  
  return(df)
}

test = scrape_mu_bulletin("https://bulletin.miamioh.edu/courses-instruction/bus/")

dept_abbr = c('acc', 'bus', 'isa', 'mkt')
my_urls = paste0(
  "https://bulletin.miamioh.edu/courses-instruction/", # Single chr string
  dept_abbr, # vector of four obs
  "/" # single chr string
  )

# The map functions take one or more inputs (depending on the function you are using)
# In this example, we only have 1 input for our functions
# So we used map_() instead of map2_() [2 is if you have two inputs], p_map()
#[for three or more inputs]
# .x = the vector you are iterating over

courses_df_from_purrr = purrr::map_df(.x = my_urls, .f = scrape_mu_bulletin)

head(courses_df_from_purrr)
```
















